### 2022-12-09 dissertation/appendix/symbols.tex
✨ (symbols): Chapter 2 done

\section{Chapter~\ref{chap:introduction}: Introduction}
\label{sec:symbols:introduction}

@@

\begin{description}
	\item
	      [\parbox{1cm}{$\alpha$}] Control parameter for leaky ReLU that controls non-zero gradients. (See Eq.~\eqref{eq:an_function_mapping} p.~\pageref{eq:an_function_mapping})
\end{description}

@@

@@

@@

@@

@@

@@

\section{Chapter~\ref{chap:conclusion}: Conclusion}
\label{sec:symbols:conclusion}

>>>>

@@

\begin{description}
	% \item
	%       [\parbox{1cm}{$EXAMPLE$}] THIS IS AN EXAMPLE DESCRIPTION. \lbrack Eq.~\eqref{eq:an_function_mapping} pg.~\pageref{eq:an_function_mapping} \rbrack

	\item [\parbox{1cm}{$I$}] The input pattern's dimension size.
	\item [\parbox{1cm}{$T$}] The target pattern's dimension size.
	\item [\parbox{1cm}{$\mathbb{R}$}] The real-number space.
	\item [\parbox{1cm}{$\mathbb{R}^{I}$}] The real-number space in I dimensions.
	\item [\parbox{1cm}{$\mathbb{R}^{T}$}] The real-number space in T dimensions.
	\item [\parbox{1cm}{$f_{AN}$}] The mapping function realised by the \acs{AN}.
	\item [\parbox{1cm}{$\boldsymbol{x}$}] The input pattern/vector.
	\item [\parbox{1cm}{$x_{i}$}] The $i$-th dimension of the input pattern/vector.
	\item [\parbox{1cm}{$\theta$}] The bias unit.
	\item [\parbox{1cm}{$\boldsymbol{v}$}] The weight vector.
	\item [\parbox{1cm}{$v_{i}$}] The $i$-th dimension of the weight vector.
	\item [\parbox{1cm}{$net$}] The net input signal to the \acs{AN}.
	\item [\parbox{1cm}{$f(net)$}] The activation function over net input signal.
	\item [\parbox{1cm}{$\boldsymbol{y}$}] The output vector.
	\item [\parbox{1cm}{$\boldsymbol{y}_{p}$}] The output vector for pattern $p$.
	\item [\parbox{1cm}{$k$}] Index for the output vector.
	\item [\parbox{1cm}{$x_{i,p}^{'}$}] The normalised form of the input at dimension $i$, pattern $p$.
	\item [\parbox{1cm}{$x_{i,p}$}] The original input at dimension $i$, pattern $p$.
	\item [\parbox{1cm}{$x_{i_{min}}$}] The input's minimum value at dimension $i$.
	\item [\parbox{1cm}{$x_{i_{max}}$}] The input's maximum value at dimension $i$.
	\item [\parbox{1cm}{$p$}] Index for the input data patterns.
	\item [\parbox{1cm}{$P$}] Total number of input data patterns.
	\item [\parbox{1cm}{$\boldsymbol{x}_p$}] The $p$-th input vector/pattern.
	\item [\parbox{1cm}{$\mu_i$}] The mean of the input at dimension $i$.
	\item [\parbox{1cm}{$\sigma^2_i$}] The unit variance of the input at dimension $i$.
	\item [\parbox{1cm}{$i$}] Index for the input vector.
	\item [\parbox{1cm}{$\omega$}] The general weight vector used for normalisation.
	\item [\parbox{1cm}{$\omega_{i}$}] The general weight vector used for normalisation at dimension $i$.
	\item [\parbox{1cm}{$\omega_{min}$}] The lower bound of the uniform distribution used for weights initialisation.
	\item [\parbox{1cm}{$\omega_{max}$}] The upper bound of the uniform distribution used for weights initialisation.
	\item [\parbox{1cm}{\footnotesize{$fanin$}}] The number of input neurons to the weight vector.
	\item [\parbox{1cm}{\footnotesize{$fanout$}}] The number of output neurons from the weight vector.
	\item [\parbox{1cm}{$\sigma$}] The standard deviation of the truncated normal distribution used for weight initialisation.
	\item [\parbox{1cm}{$K$}] Number of output units.
	\item [\parbox{1cm}{$x_{i+1}$}] The $i+1$-th dimension of the input pattern/vector.
	\item [\parbox{1cm}{$v_{i+1}$}] The $i+1$-th dimension of the weight vector.
	\item [\parbox{1cm}{$net^{'}$}] The augmented net input signal that includes the bias term.
	\item [\parbox{1cm}{$\tau$}] Phase shift threshold parameter.
	\item [\parbox{1cm}{$f(x)$}] The function used to describe the \acs{LReLU} activation function.
	\item [\parbox{1cm}{$f$}] A shorted form of the activation function.
	\item [\parbox{1cm}{$x^{+}$}] The positive part of the input parameter's domain.
	\item [\parbox{1cm}{$\alpha$}] Scaling parameter used by the \acs{LReLU} activation function.
	\item [\parbox{1cm}{$\lambda$}] Scaling/control parameter used by the sigmoid and tanh activation functions.
	\item [\parbox{1cm}{$x_{min}$}] The input's minimum value used by the min-max scaler.
	\item [\parbox{1cm}{$x_{max}$}] The input's maximum value used by the min-max scaler.
	\item [\parbox{1cm}{$\mathbb{R}^{K}$}] The real-number space in $K$ dimensions.
	\item [\parbox{1cm}{$y_{k}$}] The $k$-th dimension of the output vector.
	\item [\parbox{1cm}{$y^{'}_k$}] The softmax value of the output at dimension $k$.
	\item [\parbox{1cm}{$\boldsymbol{y^{'}}$}] The softmax form of the output vector.
	\item [\parbox{1cm}{$x_{i}$}] The $i$-th dimension of the input vector.
	\item [\parbox{1cm}{$h_{j}$}] The $j$-th dimension of the hidden layer.
	\item [\parbox{1cm}{$j$}] Index used for the hidden layer.
	\item [\parbox{1cm}{$v_{i,j}$}] The weight associated with input node $x_{i}$ and the hidden node $h_{j}$.
	\item [\parbox{1cm}{$w_{j,k}$}] The weight associated with hidden node $h_{j}$ and the output node $y_{k}$.
	\item [\parbox{1cm}{$net_{i,h}$}] The net input signal at the hidden layer.
	\item [\parbox{1cm}{$net_{h,y}$}] The net input signal at the output layer.
	\item [\parbox{1cm}{$\epsilon$}] The cost/loss produced by the loss function.
	\item [\parbox{1cm}{$y_{k,p}$}] The output produced by the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
	\item [\parbox{1cm}{$\hat{y}_{k,p}$}] The target output for the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
	\item [\parbox{1cm}{$\beta$}] Mini-batch size.
	\item [\parbox{1cm}{$\mathbbm{1}$}] The indicator function.
	\item [\parbox{1cm}{$c$}] Index used for $c$-th class.
	\item [\parbox{1cm}{$C$}] Total number of classes.

\end{description}

@@

\begin{description}
	\item [\parbox{1cm}{$\alpha$}]
	\item [\parbox{1cm}{$\beta_{1}$}]
	\item [\parbox{1cm}{$\beta_{2}$}]
	\item [\parbox{1cm}{$\beta^{t}_{1}$}]
	\item [\parbox{1cm}{$\beta^{t}_{2}$}]
	\item [\parbox{1cm}{$\beta$}]
	\item [\parbox{1cm}{$\boldsymbol{\hat{y}}_{i}(t)$}]
	\item [\parbox{1cm}{$\boldsymbol{G_{t}}$}]
	\item [\parbox{1cm}{$\boldsymbol{g}_{t}^{2}$}]
	\item [\parbox{1cm}{$\boldsymbol{g}_{t}$}]
	\item [\parbox{1cm}{$\boldsymbol{g}^{2}_{t}$}]
	\item [\parbox{1cm}{$\boldsymbol{g}$}]
	\item [\parbox{1cm}{$\boldsymbol{m}_{t}$}]
	\item [\parbox{1cm}{$\boldsymbol{m}_{t+1}$}]
	\item [\parbox{1cm}{$\boldsymbol{r}_{1} \sim U(0,1)^J$}]
	\item [\parbox{1cm}{$\boldsymbol{r}_{2} \sim U(0,1)^J$}]
	\item [\parbox{1cm}{$\boldsymbol{u}_{i}(t)$}]
	\item [\parbox{1cm}{$\boldsymbol{v}_{i}(t)$}]
	\item [\parbox{1cm}{$\boldsymbol{V}_{max}$}]
	\item [\parbox{1cm}{$\boldsymbol{v}_{t}$}]
	\item [\parbox{1cm}{$\boldsymbol{v}_{t+1}$}]
	\item [\parbox{1cm}{$\boldsymbol{v}$}]
	\item [\parbox{1cm}{$\boldsymbol{w}_{t}^{2}$}]
	\item [\parbox{1cm}{$\boldsymbol{w}_{t}$}]
	\item [\parbox{1cm}{$\boldsymbol{w}_{t+1}$}]
	\item [\parbox{1cm}{$\boldsymbol{w}$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{1}}(t)$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{1}}$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{2}}(t)$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{2}}$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{3}}(t)$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{3}}$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i} \sim U(x_{min}, x_{max})$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i}(0)$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i}(t) \in \mathcal{C}(t)$}]
	\item [\parbox{1cm}{$\boldsymbol{x}_{i}(t)$}]
	\item [\parbox{1cm}{$\boldsymbol{x}'_{i}(t)$}]
	\item [\parbox{1cm}{$\boldsymbol{y}_{i}(0)$}]
	\item [\parbox{1cm}{$\boldsymbol{y}_{i}(t)$}]
	\item [\parbox{1cm}{$\Delta w_{i}(t)$}]
	\item [\parbox{1cm}{$\Delta$}]
	\item [\parbox{1cm}{$\emptyset$}]
	\item [\parbox{1cm}{$\epsilon_{T_{p}}$}]
	\item [\parbox{1cm}{$\epsilon_{T}$}]
	\item [\parbox{1cm}{$\epsilon$}]
	\item [\parbox{1cm}{$\eta$}]
	\item [\parbox{1cm}{$\hat{\boldsymbol{m}}_{t}$}]
	\item [\parbox{1cm}{$\hat{\boldsymbol{v}}_{t}$}]
	\item [\parbox{1cm}{$\hat{y}_{ij}(t)$}]
	\item [\parbox{1cm}{$\hat{y}_{ij}$}]
	\item [\parbox{1cm}{$\hat{y}$}]
	\item [\parbox{1cm}{$\mathcal{C}(0)$}]
	\item [\parbox{1cm}{$\mathcal{C}(t+1)$}]
	\item [\parbox{1cm}{$\mathcal{E}$}]
	\item [\parbox{1cm}{$\mathcal{J}$}]
	\item [\parbox{1cm}{$\odot$}]
	\item [\parbox{1cm}{$c_{1}$}]
	\item [\parbox{1cm}{$c_{2}$}]
	\item [\parbox{1cm}{$E[\boldsymbol{g}^{2}]_{t - 1}$}]
	\item [\parbox{1cm}{$E[\boldsymbol{g}^{2}]_{t}$}]
	\item [\parbox{1cm}{$E[\Delta \boldsymbol{w}^{2}]_{t - 1}$}]
	\item [\parbox{1cm}{$E[\Delta \boldsymbol{w}^{2}]_{t}$}]
	\item [\parbox{1cm}{$f(\boldsymbol{x}_{i}(t))$}]
	\item [\parbox{1cm}{$f(\boldsymbol{x}'_{i}(t))$}]
	\item [\parbox{1cm}{$f(\hat{y})$}]
	\item [\parbox{1cm}{$f(x_{i})$}]
	\item [\parbox{1cm}{$f(x)$}]
	\item [\parbox{1cm}{$f(y_{i})$}]
	\item [\parbox{1cm}{$f$}]
	\item [\parbox{1cm}{$g_{t,i}$}]
	\item [\parbox{1cm}{$G_{t,i}$}]
	\item [\parbox{1cm}{$G_{t,ii}$}]
	\item [\parbox{1cm}{$g$}]
	\item [\parbox{1cm}{$i_{1}$}]
	\item [\parbox{1cm}{$i_{2}$}]
	\item [\parbox{1cm}{$i_{3}$}]
	\item [\parbox{1cm}{$i$}]
	\item [\parbox{1cm}{$I$}]
	\item [\parbox{1cm}{$j^{*}$}]
	\item [\parbox{1cm}{$j$}]
	\item [\parbox{1cm}{$J$}]
	\item [\parbox{1cm}{$k$}]
	\item [\parbox{1cm}{$m_{j}(t)$}]
	\item [\parbox{1cm}{$mathcal{J}$}]
	\item [\parbox{1cm}{$N_{t}$}]
	\item [\parbox{1cm}{$N$}]
	\item [\parbox{1cm}{$net_{p}$}]
	\item [\parbox{1cm}{$o_{k,p}^{2}$}]
	\item [\parbox{1cm}{$o_{p}$}]
	\item [\parbox{1cm}{$o_p$}]
	\item [\parbox{1cm}{$p_{c}$}]
	\item [\parbox{1cm}{$p_{m}$}]
	\item [\parbox{1cm}{$p_{r}$}]
	\item [\parbox{1cm}{$p_{x}$}]
	\item [\parbox{1cm}{$p$}]
	\item [\parbox{1cm}{$r_{1_{j}}$}]
	\item [\parbox{1cm}{$r_{2_{j}}$}]
	\item [\parbox{1cm}{$RMS$}]
	\item [\parbox{1cm}{$t_{k,p}$}]
	\item [\parbox{1cm}{$t_{p}$}]
	\item [\parbox{1cm}{$t$}]
	\item [\parbox{1cm}{$T$}]
	\item [\parbox{1cm}{$u_{ij}(t)$}]
	\item [\parbox{1cm}{$v_{ij}(t)$}]
	\item [\parbox{1cm}{$v_{ij}(t+1)$}]
	\item [\parbox{1cm}{$v_{ij}$}]
	\item [\parbox{1cm}{$V_{max,j}$}]
	\item [\parbox{1cm}{$V_{max}$}]
	\item [\parbox{1cm}{$v'_{ij}(t+1)$}]
	\item [\parbox{1cm}{$w_{i}(t-1)$}]
	\item [\parbox{1cm}{$w_{i}(t)$}]
	\item [\parbox{1cm}{$w_{i}$}]
	\item [\parbox{1cm}{$w_{i}$}]
	\item [\parbox{1cm}{$w_{t,i}$}]
	\item [\parbox{1cm}{$w_{t}$}]
	\item [\parbox{1cm}{$w_{t+1,i}$}]
	\item [\parbox{1cm}{$w_{t+1}$}]
	\item [\parbox{1cm}{$w$}]
	\item [\parbox{1cm}{$W$}]
	\item [\parbox{1cm}{$wv_{ij}(t)$}]
	\item [\parbox{1cm}{$wv_{ij}$}]
	\item [\parbox{1cm}{$x_{i}$}]
	\item [\parbox{1cm}{$x_{ij}(t)$}]
	\item [\parbox{1cm}{$x_{ij}(t+1)$}]
	\item [\parbox{1cm}{$x_{ij}$}]
	\item [\parbox{1cm}{$x_{max,j}$}]
	\item [\parbox{1cm}{$x_{min,j}$}]
	\item [\parbox{1cm}{$x'_{ij}(t)$}]
	\item [\parbox{1cm}{$x$}]
	\item [\parbox{1cm}{$y_{i}$}]
	\item [\parbox{1cm}{$y_{ij}(t)$}]
	\item [\parbox{1cm}{$y_{ij}$}]
	\item [\parbox{1cm}{$y$}]
	\item [\parbox{1cm}{$z_{i,p}$}]
	\item [\parbox{1cm}{$z$}]
\end{description}

@@

\begin{description}
	\item [\parbox{1cm}{$K$}]
\end{description}

@@

\begin{description}
	\item [\parbox{1cm}{$\alpha_{0}$}]
	\item [\parbox{1cm}{$\alpha_{1}$}]
	\item [\parbox{1cm}{$\alpha_{k}$}]
	\item [\parbox{1cm}{$\alpha_{K}$}]
	\item [\parbox{1cm}{$\alpha$}]
	\item [\parbox{1cm}{$\bar{A}$}]
	\item [\parbox{1cm}{$\beta'$ }]
	\item [\parbox{1cm}{$\beta$}]
	\item [\parbox{1cm}{$Bin$}]
	\item [\parbox{1cm}{$\boldsymbol{\alpha'}$}]
	\item [\parbox{1cm}{$\boldsymbol{\alpha}$}]
	\item [\parbox{1cm}{$\boldsymbol{\mathcal{D}}$}]
	\item [\parbox{1cm}{$\boldsymbol{\theta}$}]
	\item [\parbox{1cm}{$\boldsymbol{N}$}]
	\item [\parbox{1cm}{$\boldsymbol{x_{1}}$}]
	\item [\parbox{1cm}{$\boldsymbol{x_{i}}$}]
	\item [\parbox{1cm}{$\boldsymbol{x_{I}}$}]
	\item [\parbox{1cm}{$\boldsymbol{x}$}]
	\item [\parbox{1cm}{$\boldsymbol{X}$}]
	\item [\parbox{1cm}{$\boldsymbol{Y}$}]
	\item [\parbox{1cm}{$\emptyset$}]
	\item [\parbox{1cm}{$\Gamma'(n)$}]
	\item [\parbox{1cm}{$\Gamma(n)$}]
	\item [\parbox{1cm}{$\Gamma$}]
	\item [\parbox{1cm}{$\mathbb{R}$}]
	\item [\parbox{1cm}{$\mathbbm{1}$}]
	\item [\parbox{1cm}{$\mathcal{A}$}]
	\item [\parbox{1cm}{$\mathcal{L}$}]
	\item [\parbox{1cm}{$\overset{\text{iid}}{\sim}$}]
	\item [\parbox{1cm}{$\psi$}]
	\item [\parbox{1cm}{$\theta_{1}$}]
	\item [\parbox{1cm}{$\theta_{k}$}]
	\item [\parbox{1cm}{$\theta_{K}$}]
	\item [\parbox{1cm}{$\theta$}]
	\item [\parbox{1cm}{$A$}]
	\item [\parbox{1cm}{$B_{1}$}]
	\item [\parbox{1cm}{$B_{2}$}]
	\item [\parbox{1cm}{$B_{i}$}]
	\item [\parbox{1cm}{$B_{j}$}]
	\item [\parbox{1cm}{$B_{K}$}]
	\item [\parbox{1cm}{$B(\boldsymbol{\alpha})$}]
	\item [\parbox{1cm}{$B$}]
	\item [\parbox{1cm}{$Ber(\theta)$}]
	\item [\parbox{1cm}{$Beta$}]
	\item [\parbox{1cm}{$Bin$}]
	\item [\parbox{1cm}{$c$}]
	\item [\parbox{1cm}{$Cat$}]
	\item [\parbox{1cm}{$d$}]
	\item [\parbox{1cm}{$Dir$}]
	\item [\parbox{1cm}{$dn$}]
	\item [\parbox{1cm}{$E[{x_{k}}]$}]
	\item [\parbox{1cm}{$E[\ln(x_{k})]$}]
	\item [\parbox{1cm}{$E[\ln(x)]$}]
	\item [\parbox{1cm}{$E[x_{k}]$}]
	\item [\parbox{1cm}{$E[x]$}]
	\item [\parbox{1cm}{$f_{Ber}$}]
	\item [\parbox{1cm}{$f_{Beta}$}]
	\item [\parbox{1cm}{$f_{Bin}$}]
	\item [\parbox{1cm}{$f_{Cat}$}]
	\item [\parbox{1cm}{$f_{Dir}$}]
	\item [\parbox{1cm}{$f_{Mul}$}]
	\item [\parbox{1cm}{$f$}]
	\item [\parbox{1cm}{$F$}]
	\item [\parbox{1cm}{$g^{*}$}]
	\item [\parbox{1cm}{$g$}]
	\item [\parbox{1cm}{$i$}]
	\item [\parbox{1cm}{$I$}]
	\item [\parbox{1cm}{$j$}]
	\item [\parbox{1cm}{$K$}]
	\item [\parbox{1cm}{$k$}]
	\item [\parbox{1cm}{$K$}]
	\item [\parbox{1cm}{$M[x_{k}]$}]
	\item [\parbox{1cm}{$M[x]$}]
	\item [\parbox{1cm}{$m$}]
	\item [\parbox{1cm}{$M$}]
	\item [\parbox{1cm}{$Mul$}]
	\item [\parbox{1cm}{$N_{0}$}]
	\item [\parbox{1cm}{$N_{1}$}]
	\item [\parbox{1cm}{$N_{k}$}]
	\item [\parbox{1cm}{$N_{K}$}]
	\item [\parbox{1cm}{$n$}]
	\item [\parbox{1cm}{$N$}]
	\item [\parbox{1cm}{$p$}]
	\item [\parbox{1cm}{$S$}]
	\item [\parbox{1cm}{$v$}]
	\item [\parbox{1cm}{$x_{1}$}]
	\item [\parbox{1cm}{$x_{i,k}$}]
	\item [\parbox{1cm}{$x_{i}$}]
	\item [\parbox{1cm}{$x_{I}$}]
	\item [\parbox{1cm}{$x_{j}$}]
	\item [\parbox{1cm}{$x_{k}$}]
	\item [\parbox{1cm}{$x_{K}$}]
	\item [\parbox{1cm}{$x$}]
	\item [\parbox{1cm}{$y_{1}$}]
	\item [\parbox{1cm}{$Y_{1}$}]
	\item [\parbox{1cm}{$y_{2}$}]
	\item [\parbox{1cm}{$Y_{2}$}]
	\item [\parbox{1cm}{$y_{i}$}]
	\item [\parbox{1cm}{$Y_{i}$}]
	\item [\parbox{1cm}{$y_{n}$}]
	\item [\parbox{1cm}{$Y_{N}$}]
\end{description}

@@

\begin{description}
	\item [\parbox{1cm}{$\alpha_{1}$}]
	\item [\parbox{1cm}{$\alpha_{k}$}]
	\item [\parbox{1cm}{$\alpha_{K}$}]
	\item [\parbox{1cm}{$\alpha$}]
	\item [\parbox{1cm}{$\beta_{1}$}]
	\item [\parbox{1cm}{$\beta_{2}$}]
	\item [\parbox{1cm}{$\beta_{j,k}$}]
	\item [\parbox{1cm}{$\beta_{K}^{J}$}]
	\item [\parbox{1cm}{$\beta$}]
	\item [\parbox{1cm}{$\boldsymbol{\alpha}$}]
	\item [\parbox{1cm}{$\boldsymbol{\beta}$}]
	\item [\parbox{1cm}{$\boldsymbol{\gamma}$}]
	\item [\parbox{1cm}{$\boldsymbol{\hat{\phi}}$}]
	\item [\parbox{1cm}{$\boldsymbol{\hat{\psi}}$}]
	\item [\parbox{1cm}{$\boldsymbol{\hat{\theta}}$}]
	\item [\parbox{1cm}{$\boldsymbol{\lambda}$}]
	\item [\parbox{1cm}{$\boldsymbol{\phi}$}]
	\item [\parbox{1cm}{$\boldsymbol{\psi}$}]
	\item [\parbox{1cm}{$\boldsymbol{\theta}$}]
	\item [\parbox{1cm}{$\boldsymbol{C}$}]
	\item [\parbox{1cm}{$\boldsymbol{E}$}]
	\item [\parbox{1cm}{$\boldsymbol{H}$}]
	\item [\parbox{1cm}{$\epsilon(-1)$}]
	\item [\parbox{1cm}{$\epsilon$}]
	\item [\parbox{1cm}{$\eta$}]
	\item [\parbox{1cm}{$\gamma_{0}$}]
	\item [\parbox{1cm}{$\gamma_{1,k}$}]
	\item [\parbox{1cm}{$\gamma_{1}$}]
	\item [\parbox{1cm}{$\gamma_{2,k}$}]
	\item [\parbox{1cm}{$\gamma_{K}$}]
	\item [\parbox{1cm}{$\hat{\phi}_{j,k}$}]
	\item [\parbox{1cm}{$\hat{\psi_{k}}$}]
	\item [\parbox{1cm}{$\hat{\psi}_{k}$}]
	\item [\parbox{1cm}{$\hat{\theta_{k}}$}]
	\item [\parbox{1cm}{$\hat{\theta}_{k}$}]
	\item [\parbox{1cm}{$\lambda_{1}$}]
	\item [\parbox{1cm}{$\lambda_{j}$}]
	\item [\parbox{1cm}{$\lambda_{J}$}]
	\item [\parbox{1cm}{$\mathbbm{1}_{0}$}]
	\item [\parbox{1cm}{$\mathbbm{1}_{1}$}]
	\item [\parbox{1cm}{$\mathbin{\%}$}]
	\item [\parbox{1cm}{$\mathcal{A}(v)$}]
	\item [\parbox{1cm}{$\mathcal{L}$}]
	\item [\parbox{1cm}{$\phi_{j,k}$}]
	\item [\parbox{1cm}{$\phi_{jk}$}]
	\item [\parbox{1cm}{$\phi$}]
	\item [\parbox{1cm}{$\psi_{k}$}]
	\item [\parbox{1cm}{$\psi_{k}N_{k}$}]
	\item [\parbox{1cm}{$\psi$}]
	\item [\parbox{1cm}{$\theta_{k}$}]
	\item [\parbox{1cm}{$\theta$}]
	\item [\parbox{1cm}{$A$}]
	\item [\parbox{1cm}{$B$}]
	\item [\parbox{1cm}{$Beta$}]
	\item [\parbox{1cm}{$Bin$}]
	\item [\parbox{1cm}{$c_{1}$}]
	\item [\parbox{1cm}{$c_{i,k}$}]
	\item [\parbox{1cm}{$c_{i}$}]
	\item [\parbox{1cm}{$Dir$}]
	\item [\parbox{1cm}{$e_{i,j,k}$}]
	\item [\parbox{1cm}{$e_{i}$}]
	\item [\parbox{1cm}{$e_{j}$}]
	\item [\parbox{1cm}{$E[\phi_{j,k}]$}]
	\item [\parbox{1cm}{$E[\psi_{k}]$}]
	\item [\parbox{1cm}{$E[\theta_{k}]$}]
	\item [\parbox{1cm}{$h_{i,k}$}]
	\item [\parbox{1cm}{$h_{i}$}]
	\item [\parbox{1cm}{$h_{k}$}]
	\item [\parbox{1cm}{$i$}]
	\item [\parbox{1cm}{$I$}]
	\item [\parbox{1cm}{$j$}]
	\item [\parbox{1cm}{$J$}]
	\item [\parbox{1cm}{$K-1$}]
	\item [\parbox{1cm}{$k$}]
	\item [\parbox{1cm}{$K$}]
	\item [\parbox{1cm}{$L$}]
	\item [\parbox{1cm}{$LSE$}]
	\item [\parbox{1cm}{$Mult$}]
	\item [\parbox{1cm}{$N_{0,k}$}]
	\item [\parbox{1cm}{$N_{1,k}$}]
	\item [\parbox{1cm}{$N_{j,k}$}]
	\item [\parbox{1cm}{$N_{j}$}]
	\item [\parbox{1cm}{$N_{k}$}]
	\item [\parbox{1cm}{$N$}]
	\item [\parbox{1cm}{$S$}]
	\item [\parbox{1cm}{$t$}]
\end{description}

@@

\begin{description}
	\item [\parbox{1cm}{$\alpha$}]
	\item [\parbox{1cm}{$\eta$}]
	\item [\parbox{1cm}{$\mathbb{R}$}]
	\item [\parbox{1cm}{$v_{ij}$}]
	\item [\parbox{1cm}{$x_{ij}$}]

\end{description}

@@

\begin{description}
	\item [\parbox{1cm}{$\alpha_{0}$}]
	\item [\parbox{1cm}{$\alpha_{6}$}]
	\item [\parbox{1cm}{$\alpha_{7}$}]
	\item [\parbox{1cm}{$\alpha_{8}$}]
	\item [\parbox{1cm}{$\alpha_{i} = 50$}]
	\item [\parbox{1cm}{$\boldsymbol{{H}}$}]
	\item [\parbox{1cm}{$\boldsymbol{\alpha}$}]
	\item [\parbox{1cm}{$\boldsymbol{\phi}$}]
	\item [\parbox{1cm}{$\boldsymbol{\psi}$}]
	\item [\parbox{1cm}{$\boldsymbol{\theta}$}]
	\item [\parbox{1cm}{$\boldsymbol{C}$}]
	\item [\parbox{1cm}{$\boldsymbol{E}$}]
	\item [\parbox{1cm}{$\boldsymbol{H}$}]
	\item [\parbox{1cm}{$\pm$}]
	\item [\parbox{1cm}{$\theta_{0}$}]
	\item [\parbox{1cm}{$\theta_{6}$}]
	\item [\parbox{1cm}{$\theta_{7}$}]
	\item [\parbox{1cm}{$\theta_{8}$}]
	\item [\parbox{1cm}{$c_{1}$}]
	\item [\parbox{1cm}{$Cat$}]
	\item [\parbox{1cm}{$Dir$}]
	\item [\parbox{1cm}{$e_{0}$}]
	\item [\parbox{1cm}{$h_{0}$}]
	\item [\parbox{1cm}{$h_{6}$}]
	\item [\parbox{1cm}{$h_{7}$}]
	\item [\parbox{1cm}{$h_{8}$}]
	\item [\parbox{1cm}{$i$}]
	\item [\parbox{1cm}{$K$}]
\end{description}

### 2022-12-09 dissertation/chapters/02-artificial-neural-networks.tex
✨ (symbols): Chapter 2 done

\index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $w_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution. Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$~\cite{ref:nguyen:1990}.

@@

\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling, whereby $\omega = \sqrt{\frac{6}{fanin + fanout}}$ and $fanin$ is the number of input neurons to the weight vector and $fanout$ is the number of output neurons from the weight vector.

>>>>

\index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $omega_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution. Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$~\cite{ref:nguyen:1990}.

@@

\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling, whereby $\omega_{i} = \sqrt{\frac{6}{fanin + fanout}}$ and $fanin$ is the number of input neurons to the weight vector and $fanout$ is the number of output neurons from the weight vector.
